Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed title, abstract and introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
Software verification is on the core of many automated formal synthesis techniques;
it is used to formally check whether an intricate property hols for a given software system. 
Our main focus here is on using software verifiers to formally synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems. 
There exist various state-of-the-art tools to evaluate PV designs but  they are mainly based on simulations, which do not cover all aspects of the design-space. 
The application of software verification to synthesize PV systems is a very recent subject with only a few initiatives. 
Here we develop and evaluate an automated formal synthesis algorithm and report preliminary results 
using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system. 
Commercial equipment data is part of our specification and the technical solution is derived 
from financial analysis of the obtained sizing. Our proposed synthesis method is novel and 
unprecedented to streamline the design of PV systems. 
Experimental results show that our method allied to a software verifier (CPAchecker) 
is able to synthesize,in an acceptable run-time, the optimal PV system sizing of two different case studies from a list of $12$ 
different equipment.
\end{abstract}

>>>>

\begin{abstract}
Software verification is on the core of many automated formal synthesis techniques;
it is used to formally check whether an intricate property hols for a given system. 
Here our main focus is to formally synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems
using software model checking techniques. There exist various state-of-the-art tools to evaluate 
PV designs but  they are mainly based on simulations, which do not cover all aspects of the design-space. 
The application of software verification to synthesize PV systems is a very recent subject with only a few initiatives. 
Here we develop and evaluate an automated formal synthesis algorithm and report preliminary results 
using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system. 
Commercial equipment data is provided to our synthesis engine and the candidate solution is derived 
from financial analysis of the obtained sizing. Our proposed synthesis method is novel and 
unprecedented to streamline the design of PV systems. 
Experimental results show that our synthesis method based on software verification is able to synthesize, 
in an acceptable run-time, the optimal PV system sizing of two different case studies.
\end{abstract}
